The Inner Mass-Ratio Distribution of Intermediate-Mass Stars

### 2016-02-26 paper/ms.tex
Expanded on spectroscopic follow-up section.

We give the spectroscopic observation log in Table \ref{tab:observations}. We calculate the signal-to-noise ratio (the "snr" column) for the optical instruments (CHIRON, TS23, and HRS) as the median of the extracted flux divided by it's uncertainty for each pixel from the \'echelle order nearest $675$ nm. For the IGRINS instrument, we calculate the signal-to-noise ratio from the order nearest $2200$ nm.

@@

Most of the detected companions have follow-up spectra to confirm the existence of the companion. In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background contaminant (See Figure \ref{fig:ccf}). In addition we obtained Gemini/NIRI adaptive optics imaging data for 19 of the northern companions, and were able to resolve 7 of them. We show the separation, position angle, and magnitude difference in Table \ref{tab:imaging_obs}, and display the images in Figure \ref{fig:images}. One star, HIP 88116, has several nearby sources in the image. We quote the magnitude difference and separation of the brightest source in Table \ref{tab:imaging_obs}, but stress that \emph{none} of the visible sources is likely to be the companion we see in the spectroscopic data. The two epochs of spectroscopic data show a radial velocity shift of $\Delta v = 30.7\ \mathrm{km\ s}^{-1}$ over the course of roughly one year; this orbital motion is much too large to allow for any of the companions visible in the image (all with separations $ > 1''$).

@@

\startdata
  HIP 22833 &  4.83 &  2015-03-29 &   50x0.3 & $0.352 +/- 0.003$ & $14.1 \pm 0.7$ & $3.04 \pm 0.06$ \\
  HIP 22958 &  5.79 &  2015-10-19 &   52x0.4 & $0.445 +/- 0.003$ & $65.0 \pm 0.3$ & $2.57 \pm 0.05$ \\
  HIP 23916 &  5.98 &  2015-04-05 &   18x1.1 & \nodata & \nodata & \nodata \\
  HIP 26093 &  5.96 &  2015-03-23 &   33x0.6 & \nodata & \nodata & \nodata \\
  HIP 26126 &  5.07 &  2015-03-29 &   40x0.4 & \nodata & \nodata & \nodata \\
  HIP 29735 &  5.10 &  2015-03-22 &   83x0.2 & \nodata & \nodata & \nodata \\
  HIP 31278 &  5.46 &  2015-03-28 &   29x0.6 & \nodata & \nodata & \nodata \\
  HIP 38538 &  4.66 &  2015-10-19 &   75x0.2 & \nodata & \nodata & \nodata \\
  HIP 39847 &  4.66 &  2015-03-27 &   50x0.3 & \nodata & \nodata & \nodata \\
  HIP 75178 &  5.49 &  2015-03-24 &   29x0.6 & \nodata & \nodata & \nodata \\
  HIP 88116 &  4.47 &  2015-03-22 &   50x0.3 & $3.260 +/- 0.001$ & $59.29 \pm 0.02$ & $3.9 \pm 0.4$ \\
  HIP 91118 &  5.67 &  2015-10-16 &   43x0.4 & $0.1667 +/- 0.0007$ & $41.7 \pm 0.2$ & $1.77 \pm 0.01$ \\
 HIP 100221 &  5.70 &  2015-10-18 &   26x0.7 & $0.250 +/- 0.002$ & $346.8 \pm 0.92$ & $2.28 \pm 0.04$ \\
 HIP 100907 &  5.41 &  2015-10-16 &   43x0.4 & $0.463 +/- 0.002$ & $335.4 \pm 0.30$ & $2.91 \pm 0.04$ \\
 HIP 101909 &  $6.47^{\dagger}$ &  2015-10-16 &   39x0.5 & \nodata & \nodata & \nodata \\
 HIP 109139 &  4.40 &  2015-04-26 &   50x0.3 & \nodata & \nodata & \nodata \\
 HIP 109521 &  4.96 &  2015-04-25 &   40x0.4 & \nodata & \nodata & \nodata \\
 HIP 115115 &  4.96 &  2015-10-18 &   40x0.4 & $1.497 +/- 0.002$ & $313.14 \pm 0.08$ & $2.54 \pm 0.04$ \\
 HIP 118243 &  $5.87^{\dagger}$ &  2015-07-23 &   58x0.3 & $4.082 +/- 0.002$ & $310.23 \pm 0.03$ & $2.20 \pm 0.03$
\enddata
\tablecomments{$\dagger$: There is no K-magnitude tabulated in the Simbad Database. The value quoted here is estimated from the spectral type of the star and its V-band magnitude.}
\label{tab:imaging_obs}
\end{deluxetable*}

@@

  HIP 23916 & Aa,Ab$^{\dagger}$ &     1 & yes &  $5450 \pm 158$ &       5 &    -0.5  &  $1.1^{+0.20}_{-0.20}$ &  $0.9^{+0.04}_{-0.03}$ \\

>>>>

We give the spectroscopic observation log in Table \ref{tab:observations}. We calculate the signal-to-noise ratio (the ``snr'' column) for the optical instruments (CHIRON, TS23, and HRS) as the median of the extracted flux divided by it's uncertainty for each pixel from the \'echelle order nearest $675$ nm. For the IGRINS instrument, we calculate the signal-to-noise ratio from the order nearest $2200$ nm.

@@

We have follow-up spectroscopy for 17/27 of the new companions to confirm their existence. In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background contaminant (See Figure \ref{fig:ccf}). Two of the new detections (companions to HIPs 38593 and 79404) were detected twice but not in a third attempt, most likely because the third spectrum had low signal-to-noise. The companion to HIP 93805, at $\sim 4000$ K, was detected twice with near-infrared IGRINS but not the optical CHIRON instrument that is less sensitive to cool companions than IGRINS. Two of the companions with only one detection were observed at least twice (HIPs 19949 and HIP 23362); both of the non-detections are from the IGRINS instrument, which is less sensitive to hot companions with rapid rotation speeds because there are far fewer spectral lines of the companion in the near-infrared than there are in the optical.

In addition we obtained Gemini/NIRI adaptive optics imaging data for 18 of the northern companions, and were able to resolve 7 of them. We show the separation, position angle, and magnitude difference in Table \ref{tab:imaging_obs}, and display the images in Figure \ref{fig:images}. One star, HIP 88116, has several nearby sources in the image. We quote the magnitude difference and separation of the brightest source in Table \ref{tab:imaging_obs}, but stress that \emph{none} of the visible sources is likely to be the companion we see in the spectroscopic data. The two epochs of spectroscopic data show a radial velocity shift of $\Delta v = 30.7\ \mathrm{km\ s}^{-1}$ over the course of roughly one year; this orbital motion is much too large to allow for any of the companions visible in the image (all with separations $ > 1''$).

@@

\startdata
  HIP 22833 &  4.83 &  2015-03-29 &   50x0.3 & $0.352 +/- 0.003$ & $14.1 \pm 0.7$ & $3.04 \pm 0.06$ \\
  HIP 22958 &  5.79 &  2015-10-19 &   52x0.4 & $0.445 +/- 0.003$ & $65.0 \pm 0.3$ & $2.57 \pm 0.05$ \\
  HIP 26093 &  5.96 &  2015-03-23 &   33x0.6 & \nodata & \nodata & \nodata \\
  HIP 26126 &  5.07 &  2015-03-29 &   40x0.4 & \nodata & \nodata & \nodata \\
  HIP 29735 &  5.10 &  2015-03-22 &   83x0.2 & \nodata & \nodata & \nodata \\
  HIP 31278 &  5.46 &  2015-03-28 &   29x0.6 & \nodata & \nodata & \nodata \\
  HIP 38538 &  4.66 &  2015-10-19 &   75x0.2 & \nodata & \nodata & \nodata \\
  HIP 39847 &  4.66 &  2015-03-27 &   50x0.3 & \nodata & \nodata & \nodata \\
  HIP 75178 &  5.49 &  2015-03-24 &   29x0.6 & \nodata & \nodata & \nodata \\
  HIP 88116 &  4.47 &  2015-03-22 &   50x0.3 & $3.260 +/- 0.001$ & $59.29 \pm 0.02$ & $3.9 \pm 0.4$ \\
  HIP 91118 &  5.67 &  2015-10-16 &   43x0.4 & $0.1667 +/- 0.0007$ & $41.7 \pm 0.2$ & $1.77 \pm 0.01$ \\
 HIP 100221 &  5.70 &  2015-10-18 &   26x0.7 & $0.250 +/- 0.002$ & $346.8 \pm 0.92$ & $2.28 \pm 0.04$ \\
 HIP 100907 &  5.41 &  2015-10-16 &   43x0.4 & $0.463 +/- 0.002$ & $335.4 \pm 0.30$ & $2.91 \pm 0.04$ \\
 HIP 101909 &  $6.47^{\dagger}$ &  2015-10-16 &   39x0.5 & \nodata & \nodata & \nodata \\
 HIP 109139 &  4.40 &  2015-04-26 &   50x0.3 & \nodata & \nodata & \nodata \\
 HIP 109521 &  4.96 &  2015-04-25 &   40x0.4 & \nodata & \nodata & \nodata \\
 HIP 115115 &  4.96 &  2015-10-18 &   40x0.4 & $1.497 +/- 0.002$ & $313.14 \pm 0.08$ & $2.54 \pm 0.04$ \\
 HIP 118243 &  $5.87^{\dagger}$ &  2015-07-23 &   58x0.3 & $4.082 +/- 0.002$ & $310.23 \pm 0.03$ & $2.20 \pm 0.03$
\enddata
\tablecomments{$\dagger$: There is no K-magnitude tabulated in the Simbad Database. The value quoted here is estimated from the spectral type of the star and its V-band magnitude.}
\label{tab:imaging_obs}
\end{deluxetable*}

@@
